COG-ED Manuscript

### 2022-02-15 06_Paper/COG-ED/Manuscript.Rmd
Update Manuscript.Rmd

The sample of the pilot study consisted of $N=`r length(setindex)-1`$ participants (`r round((table(data_quest$gender)[2]/(length(setindex)-1))*100, digits = 1)`% female, $M=`r round(mean(data_quest[,"age"], na.rm = TRUE), digits = 1)`$ ($SD=`r round(sd(data_quest[,"age"], na.rm = TRUE), digits = 1)`$)\ years old). <!-- This results in 2 digits after the comma, all second digits are 0, perhaps use papaja::printnum instead of round, it will still be 2 digits, but with exact numbers --> 
One participant's data was removed because they misunderstood the instruction.
Due to a technical error the subjective task load data of one participant was incomplete, so the hypotheses involving the NASA Task Load Index were analyzed with $n=`r length(setindex)-2`$ data sets.
The results showed increases in subjective and objective task load measures with higher *n*-back level.
Importantly, SVs were lower for higher *n*-back levels, but not different between 1- and 2-back, which can be considered preliminary proof-of-concept, as this phenomon can only emerge in this version of the paradigm.
The MLM revealed that *n*-back level was a reliable predictor of SV, even after controlling for declining task performance (d’ and RT) as well as correct and post-correct answers, while NFC was not, most likely due to the small sample size for individual differences analyses.
The specification curve analysis showed that this pattern was true for all 63 pipelines.
Finally, while the $AxAUC$ value did not predict any amount of variance in individual NFC scores, the $AUC$ of NASA-TLX scores did.
All results are detailed in the Supplementary Material.

@@

Data collection and analysis will not be performed blind to the conditions of the experiments.
We aim to conduct all analysis as described in Westbrook et al. [-@Westbrook2013], but the level of detail was not always sufficient, so there might be deviations regarding data cleaning and degrees of freedom.
The performance measure *d'* will be computed as the difference of the *z*-transformed hit rate and the *z*-transformed false alarm rate [@Macmillan1990].
Reaction time (RT) data will be trimmed by excluding all trials with responses faster than 100\ ms, as the relevant cognitive processes cannot have been completed before [@Whelan2008; @Berger2021].
Aggregated RT values will be described using the median and the median of absolute deviation ($MAD$) as robust estimates of center and variability, respectively [@Lachaud2011].
Error- and post-error trials will be excluded in repeated measures analyses of variance (rmANOVA) and controlled for in multi-level-model (MLM), because RT on the latter is longer due to more cautious behavior [@Dutilh2012; @Houtman2012].
To test our hypotheses, we will perform a series of rmANOVAs and an MLM with orthogonal sum-to-zero contrasts in order to meaningfully interpret results [@Singmann2019]. 
Declining performance will be investigated by calculating an rmANOVA with three paired contrasts comparing *d'* between two levels of 2-, 3-, and 4-back at a time.
Another rmANOVA with three paired contrasts will be computed to compare the mean RT between two levels of 2-, 3-, and 4-back at a time.
To investigate changes in NASA-TLX ratings, six rmANOVAs will be computed, one for each NASA-TLX subscale, and each with six paired contrasts comparing the ratings between two levels of 1-, 2-, 3-, and 4-back at a time.
For each ED round, SVs will be calculated by adding or subtracting 0.015625 from the last monetary value of the flexible level, depending on the participant's last choice.
Then, these final monetary values will be divided by 2€, and the SV of each level per participant will be computed by averaging all final values of each level, regardless of whether it was fixed or flexible.
An rmANOVA with six paired contrasts will be computed, comparing the SVs between two levels of 1-, 2-, 3-, and 4-back at a time.
Estimated marginal means will be used for the paired contrasts of each rmANOVA, including Tukey method for *p*-value adjustment.

>>>>

The sample of the pilot study consisted of $N=`r length(setindex)-1`$ participants (`r round((table(data_quest$gender)[2]/(length(setindex)-1))*100, digits = 1)`% female, $M=`r round(mean(data_quest[,"age"], na.rm = TRUE), digits = 1)`$ ($SD=`r round(sd(data_quest[,"age"], na.rm = TRUE), digits = 1)`$)\ years old). <!-- This results in 2 digits after the comma, all second digits are 0, perhaps use papaja::printnum instead of round, it will still be 2 digits, but with exact numbers --> 
One participant's data was removed because they misunderstood the instruction.
Due to a technical error the subjective task load data of one participant was incomplete, so the hypotheses involving the NASA Task Load Index were analyzed with $n=`r length(setindex)-2`$ data sets.
The results showed increases in subjective and objective task load measures with higher *n*-back level.
Importantly, SVs were lower for higher *n*-back levels, but not different between 1- and 2-back, which can be considered preliminary proof-of-concept, as this phenomon can only emerge in this version of the paradigm.
A multi-level model (MLM) revealed that *n*-back level was a reliable predictor of SV, even after controlling for declining task performance (d’ and RT) as well as correct and post-correct answers, while NFC was not, most likely due to the small sample size for individual differences analyses.
The specification curve analysis showed that this pattern was true for all 63 pipelines.
Finally, while the $AxAUC$ value did not predict any amount of variance in individual NFC scores, the $AUC$ of NASA-TLX scores did.
All results are detailed in the Supplementary Material.

@@

Data collection and analysis will not be performed blind to the conditions of the experiments.
We aim to conduct all analysis as described in Westbrook et al. [-@Westbrook2013], but the level of detail was not always sufficient, so there might be deviations regarding data cleaning and degrees of freedom.
The performance measure *d'* will be computed as the difference of the *z*-transformed hit rate and the *z*-transformed false alarm rate [@Macmillan1990].
Reaction time (RT) data will be trimmed by excluding all trials with responses faster than 100\ ms, as the relevant cognitive processes cannot have been completed before [@Whelan2008; @Berger2021].
Aggregated RT values will be described using the median and the median of absolute deviation ($MAD$) as robust estimates of center and variability, respectively [@Lachaud2011].
Error- and post-error trials will be excluded in repeated measures analyses of variance (rmANOVA) and controlled for in an MLM, because RT on the latter is longer due to more cautious behavior [@Dutilh2012; @Houtman2012].
To test our hypotheses, we will perform a series of rmANOVAs and an MLM with orthogonal sum-to-zero contrasts in order to meaningfully interpret results [@Singmann2019]. 
Declining performance will be investigated by calculating an rmANOVA with three paired contrasts comparing *d'* between two levels of 2-, 3-, and 4-back at a time.
Another rmANOVA with three paired contrasts will be computed to compare the mean RT between two levels of 2-, 3-, and 4-back at a time.
To investigate changes in NASA-TLX ratings, six rmANOVAs will be computed, one for each NASA-TLX subscale, and each with six paired contrasts comparing the ratings between two levels of 1-, 2-, 3-, and 4-back at a time.
For each ED round, SVs will be calculated by adding or subtracting 0.015625 from the last monetary value of the flexible level, depending on the participant's last choice.
Then, these final monetary values will be divided by 2€, and the SV of each level per participant will be computed by averaging all final values of each level, regardless of whether it was fixed or flexible.
An rmANOVA with six paired contrasts will be computed, comparing the SVs between two levels of 1-, 2-, 3-, and 4-back at a time.
Estimated marginal means will be used for the paired contrasts of each rmANOVA, including Tukey method for *p*-value adjustment.
